---
title: "Coffee Ratings"
author: "Brendi"
date: "07/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r library, include = FALSE}
library(tidyverse)
library(colormap)
library(fmsb) # for radarchart
library(ggridges)
library(grid)
library(gridExtra)
library(knitr)
library(readr)
```


```{r gettingthedata, eval = FALSE, include = FALSE}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2020-07-07')
tuesdata <- tidytuesdayR::tt_load(2020, week = 28)

coffee_ratings <- tuesdata$coffee_ratings

# Or read in the data manually

coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv') %>% 
  # US; only Hawaii produce coffee
  mutate(country_of_origin = case_when(
    country_of_origin == "United States" ~ "United States (Hawaii)",
    TRUE ~ country_of_origin
  ))
```

```{r cleaningscript, eval = FALSE, include = FALSE}
# provided @ https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-07-07
raw_arabica <- read_csv("https://raw.githubusercontent.com/jldbc/coffee-quality-database/master/data/arabica_data_cleaned.csv") %>% 
  janitor::clean_names()

raw_robusta <-
  read_csv(
    "https://raw.githubusercontent.com/jldbc/coffee-quality-database/master/data/robusta_data_cleaned.csv",
    col_types = cols(
      X1 = col_double(),
      Species = col_character(),
      Owner = col_character(),
      Country.of.Origin = col_character(),
      Farm.Name = col_character(),
      Lot.Number = col_character(),
      Mill = col_character(),
      ICO.Number = col_character(),
      Company = col_character(),
      Altitude = col_character(),
      Region = col_character(),
      Producer = col_character(),
      Number.of.Bags = col_double(),
      Bag.Weight = col_character(),
      In.Country.Partner = col_character(),
      Harvest.Year = col_character(),
      Grading.Date = col_character(),
      Owner.1 = col_character(),
      Variety = col_character(),
      Processing.Method = col_character(),
      Fragrance...Aroma = col_double(),
      Flavor = col_double(),
      Aftertaste = col_double(),
      Salt...Acid = col_double(),
      Balance = col_double(),
      Uniform.Cup = col_double(),
      Clean.Cup = col_double(),
      Bitter...Sweet = col_double(),
      Cupper.Points = col_double(),
      Total.Cup.Points = col_double(),
      Moisture = col_double(),
      Category.One.Defects = col_double(),
      Quakers = col_double(),
      Color = col_character(),
      Category.Two.Defects = col_double(),
      Expiration = col_character(),
      Certification.Body = col_character(),
      Certification.Address = col_character(),
      Certification.Contact = col_character(),
      unit_of_measurement = col_character(),
      altitude_low_meters = col_double(),
      altitude_high_meters = col_double(),
      altitude_mean_meters = col_double()
    )
  ) %>%
  janitor::clean_names() %>%
  rename(
    acidity = salt_acid,
    sweetness = bitter_sweet,
    aroma = fragrance_aroma,
    body = mouthfeel,
    uniformity = uniform_cup
  )


all_ratings <- bind_rows(raw_arabica, raw_robusta) %>%
  select(-x1) %>%
  select(total_cup_points, species, everything())

all_ratings %>%
  skimr::skim()

all_ratings %>%
  write_csv("coffee_ratings.csv")
```

```{r readindata, include = FALSE}
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv') %>% 
  # US; only Hawaii produce coffee
  mutate(country_of_origin = case_when(
    country_of_origin == "United States" ~ "United States (Hawaii)",
    TRUE ~ country_of_origin
  ))
```


# Coffee quality across different countries

### Data Exploration
```{r, include = FALSE}
coffee_ratings %>% 
  group_by(species) %>% 
  count(species)
```
- Note Species in dataset
  - Arabica: 1311 observations // Robusta 28 observations

```{r, echo = FALSE}
# Where are most samples from?
coffee_ratings %>% 
  filter(!is.na(country_of_origin)) %>% 
  group_by(country_of_origin) %>% 
  count(sort = TRUE) %>% 
  knitr::kable(caption = "where are most samples from?") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
```

### Radar/ Spider/ Polar Chart
```{r, warning = FALSE, message = FALSE}
data <- coffee_ratings %>% 
  # select; relevant quantitative variables 
  select(country_of_origin, 
         aroma, 
         flavor, 
         aftertaste, 
         acidity, 
         body, 
         balance, 
         uniformity, 
         clean_cup, 
         sweetness, 
         cupper_points) 
  
# compute median for each category; for each country
data <- data %>% 
  group_by(country_of_origin) %>% 
  filter(n() > 10) %>% # filter where coffee sample > 10
  summarise(across(.cols = where(is.numeric), .fns = median)) # summarise column where data type is numeric

# • change 1st column into rownames 
# --> *radarchart; require; all columns; be numeric
data <- data %>% 
  remove_rownames %>% 
  column_to_rownames(var = "country_of_origin")

# •insert 1st 2 rows to be max & min of variable 
data <- rbind(rep(10, 10), rep(0, 10), data)
```

```{r, out.height = "400%", fig.width = 10}
# •specify polygon fill colour (brown coffee colour)
col2rgb("#8b4513") # find rgb of brown @ https://www.colorhexa.com/8b4513

polygon_fill <- rgb(139, 69, 19, alpha = 0.5, maxColorValue = 140)
# OR use
polygon_fill <- adjustcolor("#8b4513", alpha.f = 0.6)



# •prepare title *displayed at top of each radarchart
title <- c("Brazil", "China", "Columbia", "Costa Rica", "El Salvador", "Ethopia", "Guatemala", "Hondurus", "India", "Indonesia", "Kenya", "Malawi", "Mexico", "Nicaragua", "Taiwan", "Tanzania", "Thailand", "Uganda", "United States (Hawaii)")

# •split the screen in 6 parts
par(mar = rep(0.8,4))
par(mfrow = c(4,6))


# •create seperate radar charts; using `for loop`
for(i in 1:19){
  radarchart(data[c(1,2,i+2),],
             #customize polygon
             pcol = "black", # polygon outline colour
             pfcol = "#8B451399", # polygon fill colour
             plwd = 2, # polygon line width/thickness
             plty = 1, # polygon line type
             
             #customize grid (the "net")
             cglcol = "black", # grid line colour
             cglty = 1, # grid line type
             axislabcol = "black", # axis label colour
             caxislabels = seq(from = 0, to = 10, by = 2.5), # axos labels 
             cglwd = 0.7, # net width
             
             #customize labels
             vlcex = 0.8, # group/category label/font size
             
             # add title
             title = title[i])
}
```

> As observed in the radarcharts above, coffee profiles (depicted by the radar chart's shape) across countries appear similar. It is hard to tell for example Ethiopia is rated the highest across most categories. 

> Median scores of each category in each country were used in the plot.


```{r}
# create radarchart; with ALL countries; on 1 radarchart

# •create colour; for each country
# -> specify polygon fill colour
polygon_fill2 <- adjustcolor("#8b4513", alpha.f = 0.1)

radarchart(data,
           axistype = 1,
           # customize polygon
           pcol = "black", # polygon outline colour
           pfcol = polygon_fill2, # polygon fill colour
           plwd = 2, # polygon line width/thickness
           plty = 1, # polygon line type
           
           #customize grid(the "net")
           cglcol = "black", # grid line colour
           cglty = 1,
           axislabcol = "black", # axis label colours
           caxislabels = seq(from = 0, to = 10, by = 2.5), # axis labels
           cglwd = 0.7, # grid/net width
           
           # cutomize labels
           vlcex = 0.8, #group/cateogry label/font size
           
           # add title
           title = "All Countries"
           )
```

> Supported by the radar chart above where radarcharts of individual countries are plotted overlapping one another, we see that there is very minor difference between countries.

> All these despite having different growing conditions such as altitude, harvesting period, types/colour of coffee beans etc.

> India scored 7.75 in sweetness while the rest of countries scored 10. 



# 1. Does processing method influence coffee flavours and quality?

[Characteristics of coffee in different processing methods](https://capecoffeebeans.co.za/blogs/cape-coffee-blog/77091524-7-factors-that-influence-coffee-flavour)  
1. Washed/Wet: Tend to have higher acidity and clarity  
2. Natural/Dry: Traditional african method, tend to have fruity flavour and low acidity; Higher risk of crop spoilage.  
3. Pulped natural/Honey: Collection of wet& dry methods  

```{r clean-proc}
proc_methods <- coffee_ratings %>%
  # Remove NA in processing methods
  filter(!is.na(processing_method),
  # Remove processing method 'other'
         !processing_method == "Other",
         species == "Arabica") %>%
  select(species, country_of_origin, processing_method:cupper_points, total_cup_points)
```


```{r proc-wider}
proc_wider <- proc_methods %>%
  # Group grade scores into one column
  ## For plotting
  pivot_longer(cols = aroma:cupper_points,
               names_to = "grade",
               values_to = "grade_score")
```

### Plot 1: Density Plot for Total Cup Points of each Processing Method

```{r proc-density, message = FALSE}
p1 <- proc_wider %>%
  ggplot(aes(x = total_cup_points,
             y = processing_method,
             fill = processing_method)) +
  xlab("Total Cup Points") +
  stat_density_ridges(quantile_lines = TRUE,
                      quantiles = 0.5,
                      scale = 0.9,
                      alpha = 0.5,
                      point_shape = '|'
                      ) +
  scale_x_continuous(breaks = seq(50, 100, by = 5),
                     labels = c(seq(50, 100, by = 5))) +
  scale_fill_manual(values = c("#bcbc8f", "#8fbc8f", "#8f8fbc", "#bc8fbc")) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  ggtitle("Total cup points distribution for each processing method") +
  theme(plot.title = element_text(size = 10, face = "bold.italic"))

p1
```

```{r proc_total_summary, message = FALSE}
# Summarise total cup points for each processing method
proc_total_summ <- proc_wider %>%
  group_by(processing_method) %>%
  summarise(count = n(),
            avg_total_cup_pts = mean(total_cup_points)) %>%
  # Round to 2 decimal places
  mutate_if(is.numeric, round, 2) 
```

### Plot 2: Lollipop chart of each grade quality of each processing method

```{r proc-summary, message = FALSE}
# Mean grade score for each processing_method
proc_summary <- proc_methods %>%
  group_by(processing_method) %>%
  summarise(across(.cols = aroma:cupper_points, .fns = mean)) %>%
  ungroup() %>%
  pivot_longer(cols = aroma:cupper_points,
               names_to = "grade",
               values_to = "avg_score")
```

```{r proc-lollipop, fig.width = 7, fig.height = 7}
p2 <- proc_summary %>%
  ggplot(aes(x = avg_score, 
                 y = processing_method,
                 colour = processing_method
                 )) +
  geom_segment(aes(x = 0,
                   xend = avg_score,
                   y = processing_method,
                   yend = processing_method),
               colour = "grey") +
  xlab("Average Score") +
  ylab("Processing Method") +
  geom_point(
             size = 8
             ) +
  geom_text(color = "white", size = 2, label = round(proc_summary$avg_score, 2)) +
  scale_colour_manual(values = c("#bcbc8f", "#8fbc8f", "#8f8fbc", "#bc8fbc")) +
  facet_wrap(~ grade,
             nrow = 5
             ) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  ggtitle("Average Grade Score for Each Processing Method") +
  theme(plot.title = element_text(size = 10, face = "bold.italic"))

p2
```

### Merging plots 1 and 2

```{r merge-plots, fig.height = 8, fig.width = 12, fig.align = "center"}
ss <- proc_total_summ %>%
  # Rename columns
  rename('Processing Method' = processing_method,
         'Coffee sampled' = count,
         'Avg Total Cup Points'= avg_total_cup_pts)

# Plot processing total cup points summary table with tableGrob
ss <- tableGrob(ss, 
                # Remove row numbers
                rows = NULL) 

## Combine plots and tables
grid.arrange(p1,
             ss,
             p2,
             ncol = 2,
             nrow = 2, 
             layout_matrix = cbind(c(1,2), 3), 
             heights = c(10, 6),
             widths = c(6, 7),
             top= grid::textGrob("Coffee Quality of Arabica Coffee Beans Across Four Processing Methods",
                                 gp=gpar(fontsize = 20, col = "#a15016", fontface="bold.italic"))
             )
```