---
title: "TTweek31"
author: "Brendi Ang"
date: "27/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include = FALSE}
library(tidyverse)
```

```{r read-data, include = FALSE}
# Read in pre-cleaned data
penguins <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv')

# Read in raw data
penguins_raw <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins_raw.csv')
```

# Data
- Contains data for 344 penguins (3 different species)
- Collected from 3 islands in Antarctica
- Culmen is the upper ridge of a bird's bill

# Research questions
- Does the body mass of penguins correlate with the size of flippers?
- Do these sizes differ for each species across different islands? What about for males& females?

## Research Q1: Does the body mass of penguins correlate with the size of flippers?

- Plot bubble graph, x-axis = length of flipper, y-axis = depth of flipper, size = body mass
- Above bubble graph, plot histogram or density graph(?)

```{r scatter-plot, warning=FALSE}
penguins %>%
  ggplot(aes(x = body_mass_g,
             colour = species)
         ) +
  # Flippers length
  geom_point(aes(y = flipper_length_mm),
             alpha = 0.5,
             size = 1) +
  stat_smooth(aes(y= flipper_length_mm),
              geom = "line",
              alpha = 0.5,
              size = 1,
              method = "lm", 
              se = FALSE) +
  # Bill depth
  geom_point(aes(y = bill_length_mm),
             alpha = 0.5) +
    stat_smooth(aes(y= bill_length_mm),
              geom = "line",
              alpha = 0.5,
              size = 1,
              method = "lm", 
              se = FALSE) +
  # Bill length 
    geom_point(aes(y = bill_depth_mm),
             alpha = 0.5) +
    stat_smooth(aes(y= bill_depth_mm),
              geom = "line",
              alpha = 0.5,
              size = 1,
              method = "lm", 
              se = FALSE) +
  facet_wrap(~ species,
             nrow = 1) +
  theme_classic() +
  theme(legend.position = "bottom")
```


```{r}
penguins_long <- penguins %>%
  pivot_longer(bill_length_mm:flipper_length_mm,
               names_to = "attributes",
               values_to = "measurement")
```

```{r scatter-plot, warning = FALSE, message = FALSE}
penguins_long %>%
  ggplot(aes(x = body_mass_g,
             y = measurement)) +
  geom_point(alpha = 0.6,
             aes(colour = species)) +
  scale_colour_manual(values = c("#d3d3d3", "#e3c5c0", "#c0e3d7")) +
  facet_wrap(~ attributes,
             scales = "free_y") +
  theme_classic() +
  theme(legend.position = "bottom") +
  stat_smooth(aes(y = measurement, colour = species),
    method = "lm", 
    geom = "line",
    size = 1) 
```

```{r density-graph}
penguins_long %>%
  ggplot() +
  ggridges::geom_density_ridges(aes(x = measurement,
                                    y = species,
                                    fill = species),
                                stat = "binline",
                                bins = 20,
                                scale = 0.9,
                                alpha = 0.8
                                ) +
  scale_fill_manual(values = c("#d3d3d3", "#e3c5c0", "#c0e3d7")) +
  facet_wrap(~ attributes,
             scales = "free") +
  theme_classic() +
  theme(legend.position = "bottom")
```



