---
title: "TTweek31"
author: "Brendi Ang"
date: "27/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include = FALSE}
library(tidyverse)
library(cowplot)
library(jpeg)
library(ggpubr)
library(ggridges)
library(gridExtra)
library(here)
```

```{r read-data, include = FALSE}
# Read in pre-cleaned data
penguins <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv')

# Read in raw data
penguins_raw <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins_raw.csv')
```

# Data
- Contains data for 344 penguins (3 different species)
- Collected from 3 islands in Antarctica
- Culmen is the upper ridge of a bird's bill

# Research questions
- Does the body mass of penguins correlate with the size of flippers?
- Do these sizes differ for each species across different islands? What about for males& females?

## Research Q: Does the body mass of penguins correlate with the size of flippers?

```{r penguins-long}
penguins_long <- penguins %>%
  pivot_longer(bill_length_mm:flipper_length_mm,
               names_to = "attributes",
               values_to = "measurement")
```

```{r scatter-plot, warning = FALSE, message = FALSE, fig.align = "center", fig.height = 6, fig.width = 10}
p1 <- penguins_long %>%
  ggplot(aes(x = body_mass_g,
             y = measurement)) +
  geom_point(alpha = 0.6,
             aes(colour = species)) +
  scale_colour_manual(values = c("#d3d3d3", "#e3c5c0", "#c0e3d7")) +
  facet_wrap(~ attributes,
             scales = "free_y") +
  labs(x = "body mass (g)",
       y = "") +
  theme_classic() +
  theme(legend.position = "none") + 
  stat_smooth(aes(y = measurement, colour = species),
    method = "lm", 
    geom = "line",
    size = 1) +
  ggtitle("Body Measurements of Adelie, Chinstrap& Gentoo Penguins by Body Mass")
```

```{r density-graph, warning = FALSE, message = FALSE, fig.align = "center", fig.height = 6, fig.width = 10}
p2 <- penguins_long %>%
  ggplot() +
  ggridges::geom_density_ridges(
    aes(x = measurement,
        y = species,
        fill = species),
    stat = "binline",
    bins = 30, 
    scale = 0.9,
    alpha = 0.8
  ) +
  scale_fill_manual(values = c("#d3d3d3", "#e3c5c0", "#c0e3d7")) +
  facet_wrap( ~ attributes,
              scales = "free") +
  labs(x = "Measurement (mm)",
       y = "") +
  theme_classic() +
  theme(legend.position = "bottom") +
  ggtitle("Density Distribution of Body Measurements of Adelie, Chinstrap& Gentoo Penguins")
```

```{r combine-graph-p1-p2, warning = FALSE, message = FALSE, fig.width = 12}
p3 <- ggpubr::ggarrange(p2, 
                        p1, 
                  common.legend = TRUE,
                  nrow = 2,
                  legend = "bottom", # Common legend
                  align = "hv") # Align plots horizontally& vertically
```

```{r include-image, fig.width = 10, fig.height = 5}
require(cowplot)

# Read in downloaded images
penguins_jpg <- jpeg::readJPEG(here::here("week31/images/penguins_heights.jpg"))

p4 <- ggdraw() +
  draw_image(penguins_jpg, height = 0.9) +
  draw_label(
    "(image extracted from https://www.bas.ac.uk/wp-content/uploads/2015/04/Penguin-heights.jpg)",
    size = 12,
    fontface = "italic",
    vjust = 32
  )
```

```{r combine-all-graphs, fig.alian = "center", fig.height = 8, fig.width = 12}
gridExtra::grid.arrange(p3, 
                        p4, 
                        ncol = 2,
                        widths = c(12,8))
```



